---
title: "Cure U01 qVOA figure"
author: "Claire Levy"
date: "June 22, 2016"
output:
  md_document:
    variant: markdown_github
---

These are figures for the cure u01 grant application. We got the data from someone else, but their graph wasn't good so I am re-making it. They sent some data+graph+info in one file and some more data in another file, so I took out just the data and put it in a single .csv file to read into R.

The first figure is data from all donors

```{r, message = FALSE, warning=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
library(swarm)
library(dplyr)
library(stringr)

#This is the data set with summarized data from each donor.
windowsFonts(Arial=windowsFont("Arial"))

all_donors_dat <- read.csv("qVOA figure/qVOA_figure_all_donors_data_only.csv")



#in order to be able to make the shape of the plot depend on whether the donor is AB9105 or some other donor, I'm adding a column to indicate that so I can refer to it in the ggplot2 call

all_donors_dat<- all_donors_dat %>%
  mutate(Detail = ifelse(Donor == "AB9105", "Yes","No"))


#I also want the points that are in both timepoints to have color and not the others so I'll make a color indicating that

all_donors_dat <- all_donors_dat %>%
  mutate(Repeat = ifelse(Donor == "SD9092", "SD9092",
                         ifelse(Donor == "JH9194", "JH9194",
                                ifelse(Donor == "GF8413","GF8413", "No Repeat"))))


#Make the timepoints factors

all_donors_dat$Timepoint <- as.factor(all_donors_dat$Timepoint)

#also FH wants there to be a dark grey strip text title like for facetted plots. There isn't anything to facet on so I'll just make a column where all entries are the text I want in the strip and then facet on that to get the strip text



all_donors_dat <- all_donors_dat %>%
  mutate(strip_text = "14 HIV+ donors \n\ on suppressive ART")


ggplot(all_donors_dat, aes(x = Timepoint, y = IUPM))+
  
  geom_point(aes(shape = Detail, color = Repeat), position = position_swarm(0.07), size = 1.5)+
  
  labs(y = "Infectious units per\nmillion CD4+ T cells")+
  
  scale_shape_manual(values = c("No" = 17, "Yes" = 1))+
  
  
  scale_color_manual(values = c("JH9194" = "#1b9e77", "SD9092" = "#d95f02", "GF8413" = "#7570b3", "No Repeat" = "black"))+
  
  guides(shape = FALSE, color = FALSE)+

  
  facet_wrap(~strip_text)+
  
  scale_y_log10(breaks = c(0.1, 1, 10),limits = c(0.1,15), labels = c("0.1","1","10"))+
  
  theme(strip.text = element_text(size = 10),
      axis.ticks.x = element_blank(),
      axis.title.y = element_text(10))



ggsave("all_donors_plot.png", dpi = 600, height= 2, width = 2.2, units = "in")



all_donors_plot

```


This is the data set with "representative viral growth" from one of the donors: AB9105. "input" is # of CD4 cells, "p24" is ng/ml p24 from ELISA. if p24 = 0.01, it was below LOD.

```{r, message = FALSE, warning=FALSE, echo=FALSE}


AB9105_dat<- read.csv("qVOA figure/qVOA_figure_AB9105_data_only.csv")


AB9105_dat$Culture<- as.factor(AB9105_dat$Culture)


#Here I am changing culture #'s 6, 7, 8, 10 to be 1,2,3,4,5 so that I can have the same colors on each of the facets. They are different because the # of input CD4 cells is different, but all are from the same pt and I don't think we need to compare bwtwn cultures. Thus the legend is probably not necessary


AB9105_dat$Culture<-AB9105_dat$Culture%>%
  str_replace("6","1")%>%
  str_replace("7","2")%>%
  str_replace("8","3")%>%
  str_replace("9","4")%>%
  str_replace("10","5")



AB9105_plot <- ggplot(AB9105_dat, aes(x = Day, y = p24))+
  geom_point(aes(color = Culture), size = 1.5)+
  geom_line(aes(group = Culture, color = Culture),size = 0.8)+
  scale_y_log10(breaks=c(0.1, 10, 1000),labels = c("0.1","10","1,000"))+
labs(y = "p24 [ ng/ml ]", x = "Days in culture")+
facet_wrap(~Input)+
scale_color_brewer(type = "qual", palette = 6 )+
theme(strip.text = element_text(size = 10))+
guides(color = FALSE)

ggsave("AB98105_plot.png", dpi = 600, height= 2, width = 3.5)


AB9105_plot


```



